\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\textheight=10in
\pagestyle{empty}
\raggedright
\usepackage[left=0.65in,right=0.65in,bottom=0.8in,top=0.8in]{geometry}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [5] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 $\cdot$ #3 $\cdot$ #4 $\cdot$ #5
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

\newcommand{\courses} [1] {
    \textbf{Relevant Courses:} #1 \\
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
    {\Huge \scshape {Mohamad Radaideh}}\\
    \texttt{momo9.rad@gmail.com} $\vert$ \texttt{613-404-7313} $\vert$ \texttt{LinkedIn - Mohamad Radaideh} $\vert$ \texttt{GitHub - momo674}
\end{center}

%==== Education ====%
\header{Education}
\textbf{Carleton University}\hfill Ottawa, ON\\
Honours B.CS in Computer Science | \textbf{GPA: 4.0} \hfill  - May 2026\\
\courses{Data Structures and Algorithms (Java), Intro to Software Engineering (C++), Systems Programming, Database Management Systems, Web Application Development, Data Science}
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Kinaxis} \hfill Ottawa, ON\\
\textit{Software Developer - Algorithms} \hfill January 2024 - Present\\
% \textit{Software Engineer} \hfill January 2024 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt

    \item Developed cutting-edge Data Server features utilizing a proprietary query language, resulting in substantial enhancements to relational database efficiency and elevating user experience.
    \item Engineered new automated testing frameworks in C\# and NUnit, enhancing software adaptability and performance, and increasing product flexibility across departments.
    % \item Directed Marvin Testing, guaranteeing software adaptability and performance in critical edge cases, thereby boosting the product's flexibility.
    \item Modernized Kinaxis's C++ core supply chain algorithms with optimization mathematics, improving efficiency by 30\% and adeptly addressing ambiguous challenges through abstract thinking.
    % \item Developed a logical testing framework enabling the creation of NUnit test cases in C\#, significantly improving the quality assurance process. 
    \item Developed robust test suites in Google Test for feature enhancements and defect resolutions, significantly elevating software quality and system stability.
    \item Facilitated Agile Scrum team collaboration through active participation in stand-ups and knowledge sharing, utilizing Git and Atlassian tools to streamline project delivery.
\end{itemize}
\textbf{Virgin Plus} \hfill Ottawa, ON\\
\textit{Technical Support Assistant} \hfill August 2023 - January 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Addressed mobile, internet, and TV service problems, significantly enhancing customer satisfaction.
    \item Collaborated with network engineers to troubleshoot complex 5G connectivity issues, contributing to enhanced network reliability and performance.
    \item 
Acquired proficiency in specialized diagnostic software, streamlining troubleshooting processes and reducing service resolution time by 20\%.
\end{itemize}
\textbf{uPrep Academy} \hfill Remote\\
\textit{Program Developer} \hfill May 2023 - Aug 2023\\
% \textit{Program Engineer} \hfill May 2023 - Aug 2023\\

\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Developed a Python-based 'Intro to Programming' course tailored for high school students, delivering content to 1000+ beginners.
    \item Uploaded essential course materials like lecture notes, assignments, and class schedules onto Moodle for easy access and organization.
\end{itemize}



\header{Projects}
\vspace{1mm}

{\textbf{University Scheduling Tool} | Java, MySQL, JavaFX}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Implemented an interactive scheduling tool for university courses, allowing students and administrators to manage semester-based time tables.
    \item Utilized Java and MySQL to manage user data and course information, enhancing system reliability and user satisfaction.
\end{itemize}
\vspace*{2mm}

{\textbf{Ottawa Weather Chatroom} | JavaScript, HTML/CSS, Node.js, Express.js}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Designed and implemented a weather-focused chatroom web application for Ottawa, leveraging Node.js and Express.js for robust backend functionality.
    \item Integrated OpenWeatherMap API via REST API with the backend server, facilitating real-time sharing and discussions of weather conditions, thereby enhancing community engagement.
\end{itemize}
\vspace*{2mm}

{\textbf{Automated Tim Hortons Order} | Python, Selenium, GoogleMapsAPI, AWS}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Crafted an automation AWS server for handling Tim Hortons orders which places an order on the user's behalf if near a desired location.
    \item Leveraged Python alongside the Selenium Library to automate coffee ordering processes, dynamically adjusting to the user's live mobile location through integration with the Google Maps API.
\end{itemize}
\vspace*{2mm}

\header{Technical Skills}
\begin{tabular}{ l l }
    \textbf{Programming Languages:} & Java, C/C++, JavaScript, Python, C\#, SQL, R         \\
    \textbf{Technologies: }         & HTML/CSS, JSON, Node.js, MongoDB, SQLite, Linux, Git, Excel \\
\end{tabular}
\vspace{2mm}
\end{document}
